---
title: "R: Time Usage By Activities"
author: "Nargis Akhter"
date: "2023/10/30"
output: html_document
---

# Capstone 1

This time-tracking dataset (country, sex) was extracted from <https://perso.telecom-paristech.fr/eagan/class/igr204/datasets> for exploring, cleaning, transformation, visualization (vis.), statistical testing, and analysis.

## Load & Clean Data

1.  Load Packages & Data

2.  Rename Column Headers

    -Change periods into underscores

    -Change double underscores to single underscores

3.  Null Values

4.  Mutate Columns

```{r}
#load packages
library(tidyverse, dplyr)
```

```{r}
#load data
time_use <- read.csv("data/time use.csv")
time_use
```

```{r}
#convert to a tibble
time_usage <- as_tibble(time_use)
view(time_usage)
```

```{r}
#check column data types
str(time_usage)
```

```{r}
class(time_usage)
```

```{r}
#rename column names 

#ridding the . and __
rename_cols <- function(x){
  names(x) <- names(x) %>% str_replace_all("\\.","_") %>% tolower()
  names(x) <- names(x) %>% str_replace_all("__","_") %>% tolower()
  return(x)
}

time_usage <- rename_cols(time_usage)
view(time_usage)
```

```{r}
#convert total column to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  total <- hours * 60 + minutes
  return(total)
}

#mutate total column
time_usage <- time_usage %>%
  mutate(total = sapply(time_usage$total, convert_time_to_minutes))
```

```{r}
#convert personal_column to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  personal_care <- hours * 60 + minutes
  return(personal_care)
}

#mutate personal_care column
time_usage <- time_usage %>%
  mutate(personal_care = sapply(time_usage$personal_care, convert_time_to_minutes))
```

```{r}
#convert sleep to total minutes

convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  sleep <- hours * 60 + minutes
  return(sleep)
}

#mutate sleep column
time_usage <- time_usage %>%
  mutate(sleep = sapply(time_usage$sleep, convert_time_to_minutes))
```

```{r}
#convert eating to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  eating <- hours * 60 + minutes
  return(eating)
}

#mutate eating column
time_usage <- time_usage %>%
  mutate(eating = sapply(time_usage$eating, convert_time_to_minutes))
```

```{r}
#convert other_and_or_unspecified_personal_cares to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  other_and_or_unspecified_personal_care <- hours * 60 + minutes
  return(other_and_or_unspecified_personal_care)
}

#mutate other_and_or_unspecified_personal_cares column
time_usage <- time_usage %>%
  mutate(other_and_or_unspecified_personal_care = sapply(time_usage$other_and_or_unspecified_personal_care, convert_time_to_minutes))
```

```{r}
#convert employment_related_activities_and_travel_as_part_of_during_main_and_second_job to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  employment_related_activities_and_travel_as_part_of_during_main_and_second_job <- hours * 60 + minutes
  return(employment_related_activities_and_travel_as_part_of_during_main_and_second_job)
}

#mutate employment_related_activities_and_travel_as_part_of_during_main_and_second_job column
time_usage <- time_usage %>%
  mutate(employment_related_activities_and_travel_as_part_of_during_main_and_second_job = sapply(time_usage$employment_related_activities_and_travel_as_part_of_during_main_and_second_job, convert_time_to_minutes))
```

```{r}
#convert main_and_second_job_and_related_travel to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  main_and_second_job_and_related_travel <- hours * 60 + minutes
  return(main_and_second_job_and_related_travel)
}

#mutate main_and_second_job_and_related_travel column
time_usage <- time_usage %>%
  mutate(main_and_second_job_and_related_travel = sapply(time_usage$main_and_second_job_and_related_travel, convert_time_to_minutes))
```

```{r}
#convert activities_related_to_employment_and_unspecified_employment to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  activities_related_to_employment_and_unspecified_employment <- hours * 60 + minutes
  return(activities_related_to_employment_and_unspecified_employment)
}

#mutate activities_related_to_employment_and_unspecified_employment column
time_usage <- time_usage %>%
  mutate(activities_related_to_employment_and_unspecified_employment = sapply(time_usage$activities_related_to_employment_and_unspecified_employment, convert_time_to_minutes))
```

```{r}
#convert study to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  study <- hours * 60 + minutes
  return(study)
}

#mutate study column
time_usage <- time_usage %>%
  mutate(study = sapply(time_usage$study, convert_time_to_minutes))
```

```{r}
#convert school_and_university_except_homework to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  school_and_university_except_homework <- hours * 60 + minutes
  return(school_and_university_except_homework)
}

#mutate school_and_university_except_homework column
time_usage <- time_usage %>%
  mutate(school_and_university_except_homework = sapply(time_usage$school_and_university_except_homework, convert_time_to_minutes))
```

```{r}
#convert homework to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  homework <- hours * 60 + minutes
  return(homework)
}

#mutate homework column
time_usage <- time_usage %>%
  mutate(homework = sapply(time_usage$homework, convert_time_to_minutes))
```

```{r}
#convert free_time_study to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  free_time_study <- hours * 60 + minutes
  return(free_time_study)
}

#mutate free_time_study column
time_usage <- time_usage %>%
  mutate(free_time_study = sapply(time_usage$free_time_study, convert_time_to_minutes))
```

```{r}
#convert household_and_family_care to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  household_and_family_care <- hours * 60 + minutes
  return(household_and_family_care)
}

#mutate household_and_family_care column
time_usage <- time_usage %>%
  mutate(household_and_family_care = sapply(time_usage$household_and_family_care, convert_time_to_minutes))
```

```{r}
#convert food_management_except_dish_washing to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  food_management_except_dish_washing <- hours * 60 + minutes
  return(food_management_except_dish_washing)
}

#mutate food_management_except_dish_washing column
time_usage <- time_usage %>%
  mutate(food_management_except_dish_washing = sapply(time_usage$food_management_except_dish_washing, convert_time_to_minutes))
```

```{r}
#convert dish_washing to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  dish_washing <- hours * 60 + minutes
  return(dish_washing)
}

#mutate dish_washing column
time_usage <- time_usage %>%
  mutate(dish_washing = sapply(time_usage$dish_washing, convert_time_to_minutes))
```

```{r}
#convert cleaning_dwelling to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  cleaning_dwelling <- hours * 60 + minutes
  return(cleaning_dwelling)
}

#mutate cleaning_dwelling column
time_usage <- time_usage %>%
  mutate(cleaning_dwelling = sapply(time_usage$cleaning_dwelling, convert_time_to_minutes))
```

```{r}
#convert household_upkeep_except_cleaning_dwelling to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  household_upkeep_except_cleaning_dwelling <- hours * 60 + minutes
  return(household_upkeep_except_cleaning_dwelling)
}

#mutate cleanhousehold_upkeep_except_cleaning_dwellinging_dwelling column
time_usage <- time_usage %>%
  mutate(household_upkeep_except_cleaning_dwelling = sapply(time_usage$household_upkeep_except_cleaning_dwelling, convert_time_to_minutes))
```

```{r}
#convert laundry to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  laundry <- hours * 60 + minutes
  return(laundry)
}

#mutate laundry column
time_usage <- time_usage %>%
  mutate(laundry = sapply(time_usage$laundry, convert_time_to_minutes))
```

```{r}
#convert ironing to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  ironing <- hours * 60 + minutes
  return(ironing)
}

#mutate ironing column
time_usage <- time_usage %>%
  mutate(ironing = sapply(time_usage$ironing, convert_time_to_minutes))
```

```{r}
#convert handicraft_and_producing_textiles_and_other_care_for_textiles to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  handicraft_and_producing_textiles_and_other_care_for_textiles <- hours * 60 + minutes
  return(handicraft_and_producing_textiles_and_other_care_for_textiles)
}

#mutate handicraft_and_producing_textiles_and_other_care_for_textiles column
time_usage <- time_usage %>%
  mutate(handicraft_and_producing_textiles_and_other_care_for_textiles = sapply(time_usage$handicraft_and_producing_textiles_and_other_care_for_textiles, convert_time_to_minutes))
```

```{r}
#convert gardening_other_pet_care to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  gardening_other_pet_care <- hours * 60 + minutes
  return(gardening_other_pet_care)
}

#mutate gardening_other_pet_care column
time_usage <- time_usage %>%
  mutate(gardening_other_pet_care = sapply(time_usage$gardening_other_pet_care, convert_time_to_minutes))
```

```{r}
#convert tending_domestic_animals to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  tending_domestic_animals <- hours * 60 + minutes
  return(tending_domestic_animals)
}

#mutate tending_domestic_animals column
time_usage <- time_usage %>%
  mutate(tending_domestic_animals = sapply(time_usage$tending_domestic_animals, convert_time_to_minutes))
```

```{r}
#convert caring_for_pets to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  caring_for_pets <- hours * 60 + minutes
  return(caring_for_pets)
}

#mutate caring_for_pets column
time_usage <- time_usage %>%
  mutate(caring_for_pets = sapply(time_usage$caring_for_pets, convert_time_to_minutes))
```

```{r}
#convert walking_the_dog to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  walking_the_dog <- hours * 60 + minutes
  return(walking_the_dog)
}

#mutate walking_the_dog column
time_usage <- time_usage %>%
  mutate(walking_the_dog = sapply(time_usage$walking_the_dog, convert_time_to_minutes))
```

```{r}
#convert construction_and_repairs to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  construction_and_repairs <- hours * 60 + minutes
  return(construction_and_repairs)
}

#mutate construction_and_repairs column
time_usage <- time_usage %>%
  mutate(construction_and_repairs = sapply(time_usage$construction_and_repairs, convert_time_to_minutes))
```

```{r}
#convert shopping_and_services to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  shopping_and_services <- hours * 60 + minutes
  return(shopping_and_services)
}

#mutate shopping_and_services column
time_usage <- time_usage %>%
  mutate(shopping_and_services = sapply(time_usage$shopping_and_services, convert_time_to_minutes))
```

```{r}
#convert childcare_except_teaching_reading_and_talking to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  childcare_except_teaching_reading_and_talking <- hours * 60 + minutes
  return(childcare_except_teaching_reading_and_talking)
}

#mutate childcare_except_teaching_reading_and_talking column
time_usage <- time_usage %>%
  mutate(childcare_except_teaching_reading_and_talking = sapply(time_usage$childcare_except_teaching_reading_and_talking, convert_time_to_minutes))
```

```{r}
#convert teaching_reading_and_talking_with_child to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  teaching_reading_and_talking_with_child <- hours * 60 + minutes
  return(teaching_reading_and_talking_with_child)
}

#mutate teaching_reading_and_talking_with_child column
time_usage <- time_usage %>%
  mutate(teaching_reading_and_talking_with_child = sapply(time_usage$teaching_reading_and_talking_with_child, convert_time_to_minutes))
```

```{r}
#convert household_management_and_help_family_member to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  household_management_and_help_family_member <- hours * 60 + minutes
  return(household_management_and_help_family_member)
}

#mutate household_management_and_help_family_member column
time_usage <- time_usage %>%
  mutate(household_management_and_help_family_member = sapply(time_usage$household_management_and_help_family_member, convert_time_to_minutes))
```

```{r}
#convert leisure_social_and_associative_life to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  leisure_social_and_associative_life <- hours * 60 + minutes
  return(leisure_social_and_associative_life)
}

#mutate leisure_social_and_associative_life column
time_usage <- time_usage %>%
  mutate(leisure_social_and_associative_life = sapply(time_usage$leisure_social_and_associative_life, convert_time_to_minutes))
```

```{r}
#convert organisational_work to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  organisational_work <- hours * 60 + minutes
  return(organisational_work)
}

#mutate organisational_work column
time_usage <- time_usage %>%
  mutate(organisational_work = sapply(time_usage$organisational_work, convert_time_to_minutes))
```

```{r}
#convert informal_help_to_other_households to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  informal_help_to_other_households <- hours * 60 + minutes
  return(informal_help_to_other_households)
}

#mutate informal_help_to_other_households column
time_usage <- time_usage %>%
  mutate(informal_help_to_other_households = sapply(time_usage$informal_help_to_other_households, convert_time_to_minutes))
```

```{r}
#convert participatory_activities to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  participatory_activities <- hours * 60 + minutes
  return(participatory_activities)
}

#mutate participatory_activities column
time_usage <- time_usage %>%
  mutate(participatory_activities = sapply(time_usage$participatory_activities, convert_time_to_minutes))
```

```{r}
#convert visiting_and_feasts to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  visiting_and_feasts <- hours * 60 + minutes
  return(visiting_and_feasts)
}

#mutate visiting_and_feasts column
time_usage <- time_usage %>%
  mutate(visiting_and_feasts = sapply(time_usage$visiting_and_feasts, convert_time_to_minutes))
```

```{r}
#convert other_social_life to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  other_social_life <- hours * 60 + minutes
  return(other_social_life)
}

#mutate other_social_life column
time_usage <- time_usage %>%
  mutate(other_social_life = sapply(time_usage$other_social_life, convert_time_to_minutes))
```

```{r}
#convert entertainment_and_culture to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  entertainment_and_culture <- hours * 60 + minutes
  return(entertainment_and_culture)
}

#mutate entertainment_and_culture column
time_usage <- time_usage %>%
  mutate(entertainment_and_culture = sapply(time_usage$entertainment_and_culture, convert_time_to_minutes))
```

```{r}
#convert resting to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  resting <- hours * 60 + minutes
  return(resting)
}

#mutate resting column
time_usage <- time_usage %>%
  mutate(resting = sapply(time_usage$resting, convert_time_to_minutes))
```

```{r}
#convert walking_and_hiking to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  walking_and_hiking <- hours * 60 + minutes
  return(walking_and_hiking)
}

#mutate walking_and_hiking column
time_usage <- time_usage %>%
  mutate(walking_and_hiking = sapply(time_usage$walking_and_hiking, convert_time_to_minutes))
```

```{r}
#convert sports_and_outdoor_activities_except_walking_and_hiking to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  sports_and_outdoor_activities_except_walking_and_hiking <- hours * 60 + minutes
  return(sports_and_outdoor_activities_except_walking_and_hiking)
}

#mutate sports_and_outdoor_activities_except_walking_and_hiking column
time_usage <- time_usage %>%
  mutate(sports_and_outdoor_activities_except_walking_and_hiking = sapply(time_usage$sports_and_outdoor_activities_except_walking_and_hiking, convert_time_to_minutes))
```

```{r}
#convert computer_games to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  computer_games <- hours * 60 + minutes
  return(computer_games)
}

#mutate computer_games column
time_usage <- time_usage %>%
  mutate(computer_games = sapply(time_usage$computer_games, convert_time_to_minutes))
```

```{r}
#convert reading_books to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  reading_books <- hours * 60 + minutes
  return(reading_books)
}

#mutate reading_books column
time_usage <- time_usage %>%
  mutate(reading_books = sapply(time_usage$reading_books, convert_time_to_minutes))
```

```{r}
#convert reading_except_books to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  reading_except_books <- hours * 60 + minutes
  return(reading_except_books)
}

#mutate reading_except_books column
time_usage <- time_usage %>%
  mutate(reading_except_books = sapply(time_usage$reading_except_books, convert_time_to_minutes))
```

```{r}
#convert tv_and_video to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  tv_and_video <- hours * 60 + minutes
  return(tv_and_video)
}

#mutate tv_and_video column
time_usage <- time_usage %>%
  mutate(tv_and_video = sapply(time_usage$tv_and_video, convert_time_to_minutes))
```

```{r}
#convert radio_and_music to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  radio_and_music <- hours * 60 + minutes
  return(radio_and_music)
}

#mutate radio_and_music column
time_usage <- time_usage %>%
  mutate(radio_and_music = sapply(time_usage$radio_and_music, convert_time_to_minutes))
```

```{r}
#convert unspecified_leisure to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  unspecified_leisure <- hours * 60 + minutes
  return(unspecified_leisure)
}

#mutate unspecified_leisure column
time_usage <- time_usage %>%
  mutate(unspecified_leisure = sapply(time_usage$unspecified_leisure, convert_time_to_minutes))
```

```{r}
#convert travel_except_travel_related_to_jobs to total minutes
convert_time_to_minutes <- function(time_str) {
  time_parts <- unlist(strsplit(time_str, ":"))
  hours <- as.integer(time_parts[1])
  minutes <- as.integer(time_parts[2])
  travel_except_travel_related_to_jobs <- hours * 60 + minutes
  return(travel_except_travel_related_to_jobs)
}

#mutate travel_except_travel_related_to_jobs column
time_usage <- time_usage %>%
  mutate(travel_except_travel_related_to_jobs = sapply(time_usage$travel_except_travel_related_to_jobs, convert_time_to_minutes))
```

```{r}
view(time_usage)
```

```{r}
#check for missing values
sum(is.na(time_usage))
```

```{r}
time_usage <- time_usage %>%
  drop_na()
```

```{r}
sum(is.na(time_usage))
```

```{r}
#feature engineering new column

#average personal care time
time <- time_usage %>% 
    mutate(time_usage, avg_personal_care = (personal_care + other_and_or_unspecified_personal_care) / 2)

view(time)
```

## Hypotheses

Null Hypothesis (H0): The average time spent on personal care by females is equal to or less than the average time spent by males

Alternative Hypothesis (H1): The average time spent on personal care by females is greater than the average time spent by males

## Explore

1.  View the distribution of the target column (personal_care)
2.  View the average and median time spent on personal care by gender
3.  View scatter plot of personal care time by gender

```{r}
#histogram of personal care
ggplot(time, aes(x = personal_care)) +
  geom_histogram(binwidth = 20, fill = "purple", color = "black") +
  labs(title = "Distribution of Personal Care", x = "Personal Care Time (Minutes)", y = "Frequency")
```

```{r}
mean(time$personal_care)
```

```{r}
#grouped bar plot to compare personal care time by gender
ggplot(data = time, aes(x = sex, y = personal_care, fill = sex)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.5) +
  xlab("Gender") +
  ylab("Personal Care Time (Minutes)") +
  ggtitle("Comparison of Personal Care Time by Gender") +
  scale_fill_manual(values = c("Males" = "blue", "Females" = "pink"))
```

```{r}
#average time spent on personal care by females
women_personal_care <- time[time$sex == "Females", ]

avg_women_personal_care <- mean(women_personal_care$personal_care, na.rm = TRUE)
avg_women_personal_care
```

```{r}
#average time spent on personal care by males
men_personal_care <- time[time$sex == "Males", ]

avg_men_personal_care <- mean(men_personal_care$personal_care, na.rm = TRUE)
avg_men_personal_care
```

```{r}
#boxplot of personal care
ggplot(time, aes(x = sex, y = personal_care)) +
  geom_boxplot(fill = "green", color = "black") +
  labs(title = "Median Time Spent on Personal Care by Gender", x = "Gender", y = "Personal Care Time (Minutes)")
```

```{r}
#median time spent on personal care by females
women_personal_care <- time[time$sex == "Females", ]

median_women_personal_care <- median(women_personal_care$personal_care, na.rm = TRUE)
median_women_personal_care
```

```{r}
#median time spent on personal care by males
men_personal_care <- time[time$sex == "Males", ]

median_men_personal_care <- median(men_personal_care$personal_care, na.rm = TRUE)
median_men_personal_care
```

```{r}
#scatter plot of personal care
ggplot(data = time, aes(x = sex, y = personal_care, color = sex)) +
  geom_point() +
  xlab("Gender") +
  ylab("Personal Care Time (Minutes)") +
  ggtitle("Scatter Plot of Personal Care Time by Gender")
```

## Statistical Testing

```{r}
filtered_data <- time %>%
  filter(sex %in% c("Females", "Males"))

#perform an independent two-sample t-test
t_test_result <- t.test(personal_care ~ sex, data = filtered_data)
print(t_test_result)
```

## Analyze

In summary, a p-value of 0.4698 indicates that there is no statistically significant difference in the amount of time spent on personal care between females and females. The alternative hypothesis suggests that the true difference between the two groups is not equal to 0. The confidence interval falls between roughly -14.06314 and 29.63457. This suggests that the mean difference is not statistically significant since this interval contains 0. Therefore, we fail to reject the null hypothesis.
